---
title: "class 09"
author: "Aashna Bhargava"
date: "2026-09-28"
output:
  html_document:
    toc: TRUE
    toc_float: TRUE #wanna have toc on the left side
    number_sections: TRUE #gonna call them section 1 and 2
    code_folding: show #shows or hides code
    code_download: TRUE # allows you to download the document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Robotstxt

the code chunk bellow will show the output from the [robots txt package] for th eISA course bulletin available at: https://bulletin.miamioh.edu/courses-instruction/isa/

```{r robotstxt}
robotstxt::paths_allowed(paths = "/courses-instruction/isa/", domain = "bulletin.miamioh.edu", bot = "*")
```
##Robottxt demos

From the chunk below we are allowed to scrap the [MU football wiki page] (https://en.wikipedia.org/wiki/Miami_RedHawks_football)

```{r}
robotstxt::paths_allowed(paths = "/wiki/Miami_RedHawks_football", domain = "en.wikipedia.org", bot = "*")
```
#from the example below, the 'robotstxt' response is inconsistent with what the webpage says and is incorrect. As a general bot, we are not allowed to scarpe anythign from linkedin

#if your remove slash after domain link, it'll give the right answer (false)
```{r}
robotstxt::paths_allowed(paths = "/jobs/", domain = "https://www.linkedin.com", bot = "MU")
```

```{r}
robotstxt::paths_allowed(paths = "/viewjob", domain = "https://www.indeed.com", bot = "*")
```
```{r}
robotstxt::paths_allowed(paths = "/jobs", domain = "https://www.indeed.com", bot = "*")
```

##`rvest` demo

```{r revest_demo}
isa_page_in_r = rvest::read_html("https://bulletin.miamioh.edu/courses-instruction/isa/")

#extract titles
#if all titles look the same on the page, it measn they have the same tag/class. which would allow you to extract them in one step

#highlight on website and click inspect
#then i found the part in the inspect, that was flushed containing the title
# right clicked and copied the selector
#I saw that the output from the code below just got me the 24th course, so I dropped the ':nth-child(24)` 
isa_page_in_r |> 
  rvest::html_elements(
    "#sc_sccourcesdescs > div > p.courseblocktitle > strong"
  ) |> 
  rvest::html_text2() ->isa_titles

isa_page_in_r |> 
  rvest::html_elements(".courseblocksdesc") |> 
  rvest::html_text2()->isa_descs

isa_df = data.frame(
  title = isa_titles, description = isa_descs
)
```

