---
title: "class 11"
author: "Aashna Bhargava"
date: "2026-09-30"
output:
  html_document:
    toc: TRUE
    toc_float: TRUE #wanna have toc on the left side
    number_sections: TRUE #gonna call them section 1 and 2
    code_folding: show #shows or hides code
    code_download: TRUE # allows you to download the document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Learning objectives for today
- Scrape multiple webpages using 'for' loops;
-Scrape multiple webpages using the 'purr::map_()' type functions, which would also make you write your own custom functions in R

##Extending the course Bulletin Scrape for multiple departments

For the sake of the example, let us scape the following pages: [ISA](https://bulletin.miamioh.edu/courses-instruction/isa/) and [MKT](https://bulletin.miamioh.edu/courses-instruction/mkt/). From yhr logiv showen in class,you can essentially do that for all the FSB depts.

Note that if you are doin this for just a few depts, you can just repeat your code a few times; however, this is bad practice so we will not do this in class. Software engineers tend to refer to this as: **DRY**((don't repeat yourself))
```{r bulletin}

dept_abbr = c('acc','bus','isa','mkt') #extending the example to 4 depts
#line below illustrates how the url can be constructed by pasting0 (i.e., no space) the base_url, dept_abbreviation and the forward slash


#for(counter in 1:length(dept_abbr)){
  #print(counter)
#}

#or
#went with second option to print dept abbreviation names and not by number

courses_df = data.frame() #initialize container
for(dept_name in dept_abbr){
  cat(rep("-",25))
  print(dept_name)
  dept_url = paste0(
    "https://bulletin.miamioh.edu/courses-instruction/", dept_name,"/")

#for the titles,, i will use the selector gadget and for the desc, I will use the inspector (to show you alternative CSS selectors for what we did on Mon)

webpage = rvest::read_html(dept_url)

webpage |> rvest::html_elements("strong") |> rvest::html_text2() -> titles
webpage |> 
  rvest::html_elements("#sc_sccoursedescs>div>p.courseblockdesc") |>
  rvest::html_text2()-> descs

df=data.frame(title = titles, desc = descs)
df[1,1] |> print() #showing only the first course title

courses_df = rbind(courses_df, df)
cat(rep("-",25))
}


```
##Re-examining the prior example with the `purrr` package
my preferred approach with the purrr functions is to first create my own functions and then use it within the package.

```{r}
scrape_mu_bulletin = function(dept_url){
 
webpage = rvest::read_html(dept_url)

webpage |> rvest::html_elements("strong") |> rvest::html_text2() -> titles
webpage |> 
  rvest::html_elements("#sc_sccoursedescs>div>p.courseblockdesc") |>
  rvest::html_text2()-> descs

df=data.frame(title = titles, desc = descs)

return(df)
}

test = scrape_mu_bulletin("https://bulletin.miamioh.edu/courses-instruction/bus/")

dept_abbr = c('acc','bus','isa','mkt')
my_urls = paste0(
  "https://bulletin.miamioh.edu/courses-instruction/", #single chr string
  dept_abbr, #vector of 4 obs
  "/" #single chr string
)

#the map functions take one of more inputs (depending on the function you are using)
#in this example, we only have 1 input for our function
#so we used map_() instead of map2_() [2 is if you have two inputs] p_map() [for 3 or more inputs]
#.x = the vector you are iterating over

courses_df_from_purrr = purrr::map_df(.x = my_urls, .f = scrape_mu_bulletin)
head(courses_df_from_purrr)
```
```{r}
year = 2025

crash_url = paste0('')

crash_page
```

